\documentclass[12pt,twoside,openright]{report} 

\usepackage{fourier}
\usepackage{setspace}
\usepackage{natbib}
\doublespacing



\begin{document}

\begin{titlepage}
\begin{center}

\vspace*{2cm}
\textbf{\uppercase{\large Inference of neuronal functional connectivity from partial correlations of spiking activity}}

\vspace{1.5cm}
A Dissertation Submitted to the Faculty of

\medskip
The Graduate School 

Baylor College of Medicine

\vspace{1.5cm}
In Partial Fulfillment of the 

Requirements for the Degree

of 

Doctor of Philosophy

by 

\bigskip
{\large Dimitri Yatsenko}

\vfill
Houston, Texas

September 2014

\end{center}
\end{titlepage}


%%%%%%%%% SIGNATURE PAGE

\begin{center}
\textbf{\uppercase{\large Approved by the dissertation committee}}

\vspace{9pt}
Signed \underline{\hspace{3in}}

\vspace{-9pt}
Andreas S.\ Tolias, Ph.D.

\vspace{-9pt}
Chairperson


Signed \underline{\hspace{3in}}

\vspace{-9pt}
Fabrizio Gabbiani, Ph.D.


Signed \underline{\hspace{3in}}

\vspace{-9pt}
Kre\v{s}imir Josi\`{c}, Ph.D.

Signed \underline{\hspace{3in}}

\vspace{-9pt}
Daoyun Ji, Ph.D.

Signed \underline{\hspace{3in}}

\vspace{-9pt}
Athanassios G.\ Siapas, Ph.D.


\vspace{24pt}
\textbf{\uppercase{\large Approved by the department of neuroscience}}

\vspace{9pt}
Signed \underline{\hspace{3in}}

\vspace{-9pt}
Paul J.\ Pfaffinger, Ph.D.

\vspace{-9pt}
Director of Graduate Studies

Signed \underline{\hspace{3in}}

\vspace{-9pt}
Dora E.\ Angelaki, Ph.D.

\vspace{-9pt}
Chairman of Department

\vspace{24pt}
\textbf{\uppercase{\large Approved by the dean of graduate sciences}}

\vspace{9pt}
Signed \underline{\hspace{3in}}

\vspace{-9pt}
Hiram F.\ Gilbert, Ph.D.

\vspace{6pt}
Date \underline{\hspace{3in}}

\end{center}

\section*{Acknowledgments}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgments}
My six years of graduate studies at Baylor College of Medicine have been a great privilege, challenge, and adventure. During this time, I received tremendous support from my mentors, instructors, sponsors, collaborators, labmates, administrative staff, and friends.

I am profoundly grateful to my supervisor, Dr.\ Andreas S.\ Tolias for allowing me to become part of the multidisciplinary research environment that he has built in his lab. From our first interview and throughout the many projects we have undertaken since, he has encouraged me to think boldly yet critically.  His optimism and enthusiasm made it possible to work through several uncertain phases of my projects and to define new goals.  I thank him for the freedom to explore and pursue my own ideas.

I thank the past and current members of my dissertation committee Drs.\ Fabrizio Gabbiani, Daoyun Ji, Peter Saggau, Kre\v{s}imir Josi\`c, and Athanassios G.\ Siapas  for their continued advice and guidance. In particular, Dr.\ Josi\`c became closely involved in the definition and verification of the major mathematical aspects of this dissertation. 

My owe my fellow members of the Tolias Lab for their support and contribution to this dissertation.  In particular, I thank Emmanouil Froudarakis for teaching me the surgical procedures and two-photon imaging techniques that I used throughout my studies and for sharing his data to be included in this dissertation. I also thank my former labmate Dr.\ R.\ James Cotton who, in collaboration with Prof.~Peter Saggau, developed the unique two-photon microscope for high-speed \emph{in vivo} calcium imaging that enabled the level of analysis developed in this dissertation. I am thankful to Cathryn R.\ Cadwell for providing mice with genetically labeled interneurons that were used in this work. I thank Alexander S.\ Ecker for critically examining the assumptions underlying my statistical models and helping eliminate several logical flaws early in the process. 

The early stages of this  work were supported in part by a Predoctoral Fellowship from the Theoretical and Computational Neuroscience Training Program of the Gulf Coast Consortia.  The financial support and the excellent coursework and networking opportunities organized through this fellowship were instrumental in bringing this work to fruition. I am grateful to Dr.\ Valery Kalatsky at the University of Houston who served as my co-mentor during fellowship.

I also wish to express my gratitude to the BCM Neuroscience Department for running an excellent training program with great resources and opportunities available to its students.



\begin{abstract}
\addcontentsline{toc}{chapter}{\numberline{}Abstract}

\end{abstract}

\tableofcontents

\listoffigures

%\listoftables

\chapter{Introduction}

\section{Functional connectivity and functional organization of neural circuits}

\section{Functional connectivity from calcium signals}
This work has been submitted for publication as \citep{Yatsenko:2014}

\appendix

\chapter{Cross-validation with condition specific variances}
\bibliographystyle{mystyle}
\bibliography{biblio.bib}
\addcontentsline{toc}{chapter}{\numberline{}Bibliography}

\end{document}
